Fishbase

### 2019-11-13 data-raw/fishbase.Rmd
explore column names
little stuff

```{r}
docs(table = "diet")
```

>>>>

```{r}
tables <- c("diet", "ecology", "ecosystem", "fecundity", "fooditems", "maturity", "popchar", "popgrowth", "reproduc", "spawning", "speed", "morphdat", "oxygen")
columns <- purrr::map(tables, ~docs(table = .x)$column_name) %>% unlist()
```

download all the tables
```{r}
#diet <- diet()

eco <- ecology() %>% 
  select(-c(autoctr, StockCode, EcologyRefNo, DietRemark, FoodRemark, AddRems, OutsideHost, OHRemarks, InsideHost),
                            -ends_with("Ref"), -starts_with("Associations"))

ecosys <- ecosystem() %>%
  select(EcosystemType, Salinity, Climate, Polar, Boreal, Temperate)

fec <- fecundity()

food <- fooditems()

mat <- maturity()
